Pre-/Post-Trikafta in CFRD

### 2022-02-02 Christine Chan/Pre-post Trikafta/pre_post_trikafta_merge.Rmd
Update pre_post_trikafta_merge.Rmd
relative paths

NOTE: I HAVE THE SHARED DRIVE AS S:, to change if mapped to another letter
```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
library(lubridate)
library(stringr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S://PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
}
knitr::opts_knit$set(root.dir = home_dir)
```

@@

# bmi, pulm function 577 obs
# 8 vars MRN - ID, date for visits; start - ? start of trt?, fev, bmi, height, weight, fec 
chco_bmi_pft = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_bmi_pft.csv")

# continuous glucose monitoring, 23 obs
# 105 vars subjectid - number_pre/post for visit and a date; numbers dont seem to correspond to mrn in bmi pft
chco_cgm = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_cgm.csv")

# chco glycemic, 261 obs
# 7 var MRN and CFF id (=subjectid?), date for visits; start... etc
chco_glycemic = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_glycemic.csv")

# chco registry 108 obs
# CFF ID and MRN, start date
chco_registry = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_registry.csv")
###################################

@@

# NEED TO RENAME VARIABLES TO MATCH CHCO#
# bmi, pulm function 975 obs
montana_bmi_pft <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_bmi_pft.csv")

# cgm 16 obs
montana_cgm <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_cgm.csv")

# registry: we need to combine demo (126), genotypes (126), pancreatic (241), gtubes (155)
montana_demo <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_demo.csv")
montana_genotypes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_genotypes.csv")
montana_gtubes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_gtubes.csv") # what are the dates here
montana_pancreatic <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_pancreatic.csv") # what is this? just dates and cffid
# ask tim:what do we need to do with gtubes and pancreatic dates? dont look like chco data

# glycemic 279
montana_glycemic_registry <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_glycemic_registry.csv") # looks identical
###################################

###### IMPORT UW DATA #############
uw_registry <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_registry.csv") #cffid and start
uw_bmi <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_bmi.csv") # date, cffid, height, bmi (height bmi need rename)
uw_pft <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_pft.csv") # datee, cffid, fev, fvc need renaming
uw_cgm <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_cgm.csv") # same code as montana
uw_demo <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_demo.csv") 
uw_genotypes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_registry.csv") # no genotype data here?
uw_glycemic <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_glycemic.csv") # looks good, same as chco
uw_gtubes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_gtubes.csv") # rename date of encounter to date
uw_pancreatic <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/uw_pancreatic.csv") # same as montana, no pancreatic data though

@@

###### IMPORT UM DATA ########
um_all <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/um_all.csv")
###################################

@@

# export csv analysis_data
write.csv(analysis_data, file = "S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/analysis_data.csv")
```

>>>>

NOTE: I HAVE THE SHARED DRIVE AS S:, to change if mapped to another letter
```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
library(lubridate)
library(stringr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
}
knitr::opts_knit$set(root.dir = home_dir)
```

@@

# bmi, pulm function 577 obs
# 8 vars MRN - ID, date for visits; start - ? start of trt?, fev, bmi, height, weight, fec 
chco_bmi_pft = read_csv("./Prepost Triakfta/Data_Cleaned/chco_bmi_pft.csv")

# continuous glucose monitoring, 23 obs
# 105 vars subjectid - number_pre/post for visit and a date; numbers dont seem to correspond to mrn in bmi pft
chco_cgm = read_csv("./Prepost Triakfta/Data_Cleaned/chco_cgm.csv")

# chco glycemic, 261 obs
# 7 var MRN and CFF id (=subjectid?), date for visits; start... etc
chco_glycemic = read_csv("./Prepost Triakfta/Data_Cleaned/chco_glycemic.csv")

# chco registry 108 obs
# CFF ID and MRN, start date
chco_registry = read_csv("./Prepost Triakfta/Data_Cleaned/chco_registry.csv")
###################################

@@

# NEED TO RENAME VARIABLES TO MATCH CHCO#
# bmi, pulm function 975 obs
montana_bmi_pft <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_bmi_pft.csv")

# cgm 16 obs
montana_cgm <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_cgm.csv")

# registry: we need to combine demo (126), genotypes (126), pancreatic (241), gtubes (155)
montana_demo <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_demo.csv")
montana_genotypes <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_genotypes.csv")
montana_gtubes <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_gtubes.csv") # what are the dates here
montana_pancreatic <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_pancreatic.csv") # what is this? just dates and cffid
# ask tim:what do we need to do with gtubes and pancreatic dates? dont look like chco data

# glycemic 279
montana_glycemic_registry <- read_csv("./Prepost Triakfta/Data_Cleaned/montana_glycemic_registry.csv") # looks identical
###################################

###### IMPORT UW DATA #############
uw_registry <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_registry.csv") #cffid and start
uw_bmi <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_bmi.csv") # date, cffid, height, bmi (height bmi need rename)
uw_pft <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_pft.csv") # datee, cffid, fev, fvc need renaming
uw_cgm <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_cgm.csv") # same code as montana
uw_demo <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_demo.csv") 
uw_genotypes <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_registry.csv") # no genotype data here?
uw_glycemic <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_glycemic.csv") # looks good, same as chco
uw_gtubes <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_gtubes.csv") # rename date of encounter to date
uw_pancreatic <- read_csv("./Prepost Triakfta/Data_Cleaned/uw_pancreatic.csv") # same as montana, no pancreatic data though

@@

###### IMPORT UM DATA ########
um_all <- read_csv("./Prepost Triakfta/Data_Cleaned/um_all.csv")
###################################

@@

# export csv analysis_data
write.csv(analysis_data, file = "./Prepost Triakfta/Data_Cleaned/analysis_data.csv")
```
